|

### 2021-03-12 documentation/readme.Rmd
Added title to README plot

timeplot <- 
pollbasepro %>% 
  pivot_longer(
    cols = c(-date, -election, -govt, -week, -month, -quarter, -year, -con_ldr, -lab_ldr, -lib_ldr),
    names_to = c("party", ".value"),
    names_sep = "_",
  ) %>%
  mutate(
    party =
      case_when(
        party == "con" ~ "Conservative Party",
        party == "lab" ~ "Labour Party",
        party == "lib" ~ "Liberals (Various Forms)"
      ) %>% 
      factor(
        levels = 
          c("Conservative Party",
            "Labour Party",
            "Liberals (Various Forms)"
          )
      )
  ) %>%
  ggplot(
    aes(
      x = date,
      y = est,
      ymin = est - qnorm(0.975)*err,
      ymax = est + qnorm(0.975)*err,
      colour = party,
      fill = party
    )
  ) +
  geom_ribbon(alpha = .3, colour = NA) +
  geom_line() +
  scale_colour_manual(values = pty_cols) +
  scale_fill_manual(values = pty_cols) +
  scale_y_continuous(
    breaks = seq(0, .6, by = .1),
    labels = scales::percent_format(accuracy = 1)
    ) +
  scale_x_date(
    breaks = seq.Date(as.Date("1955-01-01"), max(pollbasepro$date), by = "3 months"),
    labels = format(seq.Date(as.Date("1955-01-01"), max(pollbasepro$date), by = "3 months"), "%b %y")
    ) +
  coord_cartesian(
    ylim = c(0, 0.62),
    xlim = c(as_date("2019-12-12"), Sys.Date())
    ) +
  jbmisc::theme_bailey() +
  labs(
    colour = "Party",
    fill = "Party",
    y = "Vote Share",
    caption = "Based on data from PollBasePro, created by Jack Bailey, Mark Pack, and Luke Mansillo: www.github.com/jackobailey/PollBasePro"
  ) +
  theme(
    legend.position = "bottom",
    legend.title = element_blank(),
    axis.title.x = element_blank()
  )

>>>>

timeplot <- 
pollbasepro %>% 
  pivot_longer(
    cols = c(-date, -election, -govt, -week, -month, -quarter, -year, -con_ldr, -lab_ldr, -lib_ldr),
    names_to = c("party", ".value"),
    names_sep = "_",
  ) %>%
  mutate(
    party =
      case_when(
        party == "con" ~ "Conservative Party",
        party == "lab" ~ "Labour Party",
        party == "lib" ~ "Liberals (Various Forms)"
      ) %>% 
      factor(
        levels = 
          c("Conservative Party",
            "Labour Party",
            "Liberals (Various Forms)"
          )
      )
  ) %>%
  ggplot(
    aes(
      x = date,
      y = est,
      ymin = est - qnorm(0.975)*err,
      ymax = est + qnorm(0.975)*err,
      colour = party,
      fill = party
    )
  ) +
  geom_ribbon(alpha = .3, colour = NA) +
  geom_line() +
  scale_colour_manual(values = pty_cols) +
  scale_fill_manual(values = pty_cols) +
  scale_y_continuous(
    breaks = seq(0, .6, by = .1),
    labels = scales::percent_format(accuracy = 1)
    ) +
  scale_x_date(
    breaks = seq.Date(as.Date("1955-01-01"), max(pollbasepro$date), by = "3 months"),
    labels = format(seq.Date(as.Date("1955-01-01"), max(pollbasepro$date), by = "3 months"), "%b %y")
    ) +
  coord_cartesian(
    ylim = c(0, 0.62),
    xlim = c(as_date("2019-12-12"), Sys.Date())
    ) +
  jbmisc::theme_bailey() +
  labs(
    title = paste0("British Poll of Polls, ", str_remove(format(max(pollbasepro$date), "%d %B %Y"), "^0")),
    colour = "Party",
    fill = "Party",
    y = "Vote Share",
    caption = "Based on data from PollBasePro, created by Jack Bailey, Mark Pack, and Luke Mansillo: www.github.com/jackobailey/PollBasePro"
  ) +
  theme(
    legend.position = "bottom",
    legend.title = element_blank(),
    axis.title.x = element_blank()
  )
